### 2015-01-02 paper_10_intro.tex
reorganize the introduction

\subsection{CMMI}
The Capability Maturity Model Integration (CMMI) is one of the most widely acknowledged models for process 
improvement in software development.  CMMI offers a generic guideline and appraisal program for process 
improvement.  It was created and is administered by the Software Engineering Institute at
Carnegie Mellon University. While the CMMI is not specific to software development,
it is often applied in software development settings.
CMMI certification is required for many United States Government and Department of Defense contracts.

@@

\subsubsection{CMMI MATURITY LEVEL 1 - INITIAL}
    A maturity level 1 organization consists of a adhoc and chaotic processes.  While working
    products are still produced, the results are often over budget and behind schedule.  A level
    1 organization will also have difficulties repeating a process with the same degree of 
    success.  These organizations typically rely on the heroic efforts of certain individuals.

\subsubsection{CMMI MATURITY LEVEL 2 - MANAGED}
    A maturity level 2 organization has a policy for planning and executing processes.  
    The processes are controlled, monitored, reviewed, and enforced.  The practices are even
    maintained in times of stress.  The following process areas should be present at maturity
    level 2.
    \begin{description}
        \item Configuration Management (CM)
        \item Measurement and Analysis (MA)
        \item Project Monitoring and Control (PMC)
        \item Project Planning (PP)
        \item Process and Product Quality Assurance (PPQA)
        \item Requirements Management (REQM)
        \item Supplier Agreement Management (SAM)
    \end{description}

\subsubsection{CMMI MATURITY LEVEL 3 - DEFINED}
    A maturity level 3 organization has well-understood processes that are described in 
    standards, tools, procedures, and methods.  The organization has standard processes
    that are reviewed and improved over time.  The major differentiators between level 2 
    and level 3 is the existence of standards and process descriptions. 
    A level 2 organization will have
    processes that are inconsistent across projects.  A level 3 organization will tailor
    a standard process for each project.  Also, level 3 processes are described with 
    much more rigor.  In addition to the process areas found in level 2, 
    the following process areas should be present at maturity level 3.
    \begin{itemize}
        \item Decision Analysis and Resolution (DAR)
        \item Integrated Project Management (IPM)
        \item Organizational Process Definition (OPD)
        \item Organizational Process Focus (OPF)
        \item Organizational Training (OT)
        \item Product Integration (PI)
        \item Requirements Development (RD)
        \item Risk Management (RSKM)
        \item Technical Solution (TS)
        \item Validation (VAL)
        \item Verification (VER)
    \end{itemize}

\subsubsection{CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED}
    A maturity level 4 organization has quantitative measures for quality and process performance. 
    The measures are based upon customer needs, end users, and process implementers.  The quality
    and process performance are understood mathematically and managed throughout the life of a project.
    Level 4 is characterized by the predictability of the process performance. In addition to
    the process areas found in level 2 and 3, the following additional process areas should be present
    at maturity level 4.
    \begin{itemize}
        \item Organizational Process Performance (OPP)
        \item Quantitative Project Management (QPM)
    \end{itemize}
\subsubsection{CMMI MATURITY LEVEL 5 - OPTIMIZING} 
    The final and pinnacle level of CMMI maturity is level 5.  A maturity level 5 organization
    continually improves processes based upon quantitative measures.  The major distinction from 
    level 4 is the constant focus on improving and managing organizational performance.  A maturity level
    5 organization has well-documented standard processes that are tracked and enforced as well as
    a focus on continual improvement of the processes based upon 
    quantitative measures.  In addition to the process areas of the previous maturity levels, maturity
    level 5 should contain the following process areas.
    \begin{itemize}
        \item Causal Analysis and Resolution (CAR)
        \item Organizational Performance Management (OPM)
    \end{itemize}

@@

\subsection{PREVIOUS SOFTWARE EVALUATION ATTEMPTS }

>>>>

\subsection{OVERVIEW}

    What is the goal? how will it help?  Expand on the thesis statement here
    score the overall organization
    produce a single a number score
    don't focus too heavily on the source code

\subsection{PREVIOUS SOFTWARE EVALUATION METHODS}

While much work has been done in t

\subsubsection{CMMI}
    The Capability Maturity Model Integration (CMMI) is one of the most 
    widely acknowledged models for process 
    improvement in software development.  CMMI offers a generic guideline 
    and appraisal program for process 
    improvement.  It was created and is administered by the Software Engineering Institute at
    Carnegie Mellon University. While the CMMI is not specific to software development,
    it is often applied in software development settings.
    CMMI certification is required for many United States Government 
    and Department of Defense contracts.

@@

    \begin{description}
        \item[CMMI MATURITY LEVEL 1 - INITIAL]
            A maturity level 1 organization consists of a adhoc and chaotic processes.  While working
            products are still produced, the results are often over budget and behind schedule.  A level
            1 organization will also have difficulties repeating a process with the same degree of 
            success.  These organizations typically rely on the heroic efforts of certain individuals.

        \item[CMMI MATURITY LEVEL 2 - MANAGED]
            A maturity level 2 organization has a policy for planning and executing processes.  
            The processes are controlled, monitored, reviewed, and enforced.  The practices are even
            maintained in times of stress.  The following process areas should be present at maturity
            level 2.
            \begin{itemize}
                \item Configuration Management (CM)
                \item Measurement and Analysis (MA)
                \item Project Monitoring and Control (PMC)
                \item Project Planning (PP)
                \item Process and Product Quality Assurance (PPQA)
                \item Requirements Management (REQM)
                \item Supplier Agreement Management (SAM)
            \end{itemize}

        \item[CMMI MATURITY LEVEL 3 - DEFINED]
            A maturity level 3 organization has well-understood processes that are described in 
            standards, tools, procedures, and methods.  The organization has standard processes
            that are reviewed and improved over time.  The major differentiators between level 2 
            and level 3 is the existence of standards and process descriptions. 
            A level 2 organization will have
            processes that are inconsistent across projects.  A level 3 organization will tailor
            a standard process for each project.  Also, level 3 processes are described with 
            much more rigor.  In addition to the process areas found in level 2, 
            the following process areas should be present at maturity level 3.
            \begin{itemize}
                \item Decision Analysis and Resolution (DAR)
                \item Integrated Project Management (IPM)
                \item Organizational Process Definition (OPD)
                \item Organizational Process Focus (OPF)
                \item Organizational Training (OT)
                \item Product Integration (PI)
                \item Requirements Development (RD)
                \item Risk Management (RSKM)
                \item Technical Solution (TS)
                \item Validation (VAL)
                \item Verification (VER)
            \end{itemize}

        \item[CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED]
            A maturity level 4 organization has quantitative measures for quality and process performance. 
            The measures are based upon customer needs, end users, and process implementers.  
            The quality
            and process performance are understood mathematically and managed 
            throughout the life of a project.
            Level 4 is characterized by the predictability of the process performance. 
            In addition to
            the process areas found in level 2 and 3, the following additional 
            process areas should be present
            at maturity level 4.
            \begin{itemize}
                \item Organizational Process Performance (OPP)
                \item Quantitative Project Management (QPM)
            \end{itemize}

        \item[CMMI MATURITY LEVEL 5 - OPTIMIZING]
            The final and pinnacle level of CMMI maturity is level 5.  
            A maturity level 5 organization
            continually improves processes based upon quantitative measures.  
            The major distinction from 
            level 4 is the constant focus on improving and managing 
            organizational performance.  A maturity level
            5 organization has well-documented standard processes that are 
            tracked and enforced as well as
            a focus on continual improvement of the processes based upon 
            quantitative measures.  In addition to the process areas of the 
            previous maturity levels, maturity
            level 5 should contain the following process areas.
            \begin{itemize}
                \item Causal Analysis and Resolution (CAR)
                \item Organizational Performance Management (OPM)
            \end{itemize}
    \end{description}

@@
